\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black}
\nopagenumbers{}
\usepackage[utf8]{inputenc}
\usepackage{ragged2e}
\usepackage[scale=0.915]{geometry}
\usepackage{import}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{fontawesome5}
\usepackage[colorlinks = true,
        urlcolor  = blue,unicode]{hyperref}
\name{Ujjwal}{Chowdhury}
\newcommand*{\customcventry}[7][.13em]{
\begin{tabular}{@{}l}
{\bfseries #4} \
{\itshape #3}
\end{tabular}
\hfill
\begin{tabular}{l@{}}
{\bfseries #5} \
{\itshape #2}
\end{tabular}
\ifx&#7&%
\else{\
\begin{minipage}{\maincolumnwidth}%
\small#7%
\end{minipage}}\fi%
\par\addvspace{#1}}


\begin{document}
\makecvtitle
\vspace*{-16mm}
\begin{center}\textbf{Data Scientist, Research Analyst, Azure Certified}\end{center}
\begin{center}
\begin{tabular}{ c c c }
\faMobile\enspace +91 8768686849 & \enspace\faIcon{envelope} \href{mailto:u77w41@gmail.com}{\color{black}{u77w41@gmail.com}} & \faHome\enspace Kolkata, India \\
\faLinkedin\enspace \color{blue} \href{https://www.linkedin.com/in/u77w41/}{in/u77w41} &
\faGithub\enspace \color{blue} \href{https://github.com/u77w41}{github.com/u77w41} & \enspace {$\mathbb{X}$}\enspace \color{blue} \href{https://twitter.com/UjjwalCh0wdhury}{UjjwalCh0wdhury}
\end{tabular}
\end{center}

% \section{Profile}
% {Data Scientist with a Master\'s in Data Science and expertise in NLP, Generative AI, and Stock Forecasting. Skilled in AI solution design, ML model implementation, and cross-functional collaboration to deliver impactful insights. Proficient in process automation, outcome analysis, and effective communication for driving business success.}

% \section{Areas of Expertise}
{A quick learner and hardworking individual with a strong foundation in Data Science and Mathematics, I currently excel as an AI Research Executive. My passion lies in applying statistical methods, Machine Learning, and Deep Learning to tackle real-world challenges. Certified as a Research Analyst and Azure certified Data Scientist, I am eager to leverage my expertise in roles such as Data Scientist, Data Analyst, or any position aligned with my skill set.}

\section{Skills}
{\begin{itemize}[label=\textbullet]
\item {\textbf{Data Visualization:} Microsoft Power BI, Excel, Tableau, Seaborn, Plotly, Matplotlib.}
\item {\textbf{Machine Learning \& Deep Learning:}
Regression, Classification, Clustering,
Feature Engineering, Model Development, 
Hyper-parameter Tuning, 
Neural Networks,
RNN,
CNN,
LSTM,
Transformers,
GANs,
Reinforcement Learning,
Transfer Learning,
Optimization Techniques,
MLOps.}
\item {\textbf{Tools \& Frameworks:} 
Python,
R,
TensorFlow,
PyTorch,
Keras,
TFLite,
MLFlow,
PySpark,
PostgreSQL,
Azure,
AWS,
LangChain,
Streamlit,
Docker,
Pydantic.
}
\item {\textbf{Natural Language Processing:} Text Generation,
Sentiment Analysis,
Speech Recognition,
Named Entity Recognition,
Text Classification, LLM Prompt Engineering.}
\item {\textbf{Computer Vision:} Image Processing, Object Detection, Image Classification, Image Segmentation, Image Generation.}
\item {\textbf{Data Analysis and Mining:} Data Mining,
Web Scrapping,
Statistical Analysis,
Time Series Analysis,
Anomaly Detection,
Predictive Analytics,
Survival Analysis.}
\item {\textbf{Soft Skills:} Problem-Solving, Teamwork, Active Listening, Adaptability, Communication, Analytical Thinking.}
\end{itemize}}



\section{Professional Experience}

\customcventry{(Jan 2023 ‐ Present)}{{\color{blue}\href{https://feedsense.ai/}{Feedsense AI (Formerly Vista Intelligence)}}}{Research Executive (AI \& NLP) }{Kolkata, 
India}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Led the NLP team, driving project developments and team operations.
\item Achieved a significant reduction in Word Error Rate from 56.8\% to 23.4\% by fine-tuning an RNN-Transducer model tailored for Indian accents.
% \item Implemented a cutting-edge 4-bit quantized Mistral 7b LLM model to streamline conference call summarization processes.
\item Leveraged reinforcement learning algorithms with financial data to accurately predict market movements and formulate high-performance trading strategies.
% \item Utilized OpenAI API with Langchain to develop a large document summarizer.
\item Engineered a scalable large document summarizer using OpenAI API integrated with Langchain, enhancing operational efficiency by 40\%.
\item Developed a real-time audio transcription model for instant news analysis, improving response times by 60\%, utilizing an efficient framework built with Redis and PostgreSQL.
\item Designed and deployed a sophisticated trade signal generator combining live audio, textual news analysis, OHLC data, and quantitative techniques, achieving over 75\% accuracy in directional trading signals for Nifty F\&O, empowering informed decision-making.
\item Innovated an automated question generator program, facilitating the hiring process by generating tailored interview questions based on applicant CVs.
\item Implemented CI/CD pipelines and Docker containers to establish a streamlined model deployment process on local servers.
\item Utilized Kubernetes for orchestration and scaling of applications, integrating with time series databases for efficient data management and analysis.
\end{itemize}}}

% \customcventry{01/2023 ‐ 05/2023}{{\color{blue}\href{https://www.google.com/}{(Synapse Solutions)}}}{Digital Account Manager,}{Las Vegas, NV}{}{
% {\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
% \item Implemented promotional activities such as re-targeting campaigns for e-commerce businesses.
% \item Monitored the performance of PPC campaigns through Google Adwords. 
% \item Managed and optimized PPC campaigns, resulting in a 5\% increase in click-through rates
% \end{itemize}}}

\section{Research \& Publication}
% \customcventry{March 2024}{\color{blue}\href{https://ieeexplore.ieee.org/document/10445412?source=authoralert}{IEEE Xplore}}
% {{Investigate How Market Behaves: Toward an Explanatory Multitasking Based Analytical Model for Financial Investments}}{DOI: 10.1109/ACCESS.2024.3369033} {}{}
{\begin{itemize}[label=\textbullet]
    \item Investigate How Market Behaves: Toward an Explanatory Multitasking Based Analytical Model for Financial Investments \textit{(IEEE Access, March 2024)} \color{blue}\href{DOI: 10.1109/ACCESS.2024.3369033}{DOI: 10.1109/ACCESS.2024.3369033}
\end{itemize}}

% Investigate How Market Behaves: Toward an Explanatory Multitasking Based Analytical Model for Financial Investments



\section{Courses \& Certifications}
{\begin{itemize}[label=\textbullet]
    \item Azure Data Scientist Associate \textit{(June 2024)} - \underline{\color{blue}\href{https://learn.microsoft.com/api/credentials/share/en-us/u77w41/6DED7CA0675E173B?sharingId=2E0F4AA6DCCB6C73}{Microsoft}}
    \item Artificial Intelligence (AI) for Investments \textit{(April 2023)} - \underline{\color{blue}\href{https://onlinecourses.nptel.ac.in/noc23_mg63/preview}{NPTEL}}
    \item Cloud Computing and Distributed Systems \textit{(March 2023)} - \underline{\color{blue}\href{https://onlinecourses.nptel.ac.in/noc21_cs15/preview}{NPTEL}}
    \item NISM-Series-XV: Research Analyst \textit{(Feb. 2023)} - \underline{\color{blue}\href{https://www.nism.ac.in/}{National Institute of Securities Markets}}
    \item Data Base Management System \textit{(Oct. 2022)} - \underline{\color{blue}\href{https://onlinecourses.nptel.ac.in/noc21_cs04/preview}{NPTEL}}
    \item Deep Learning for Computer Vision \textit{(Oct. 2022)} - \underline{\color{blue}\href{https://onlinecourses.nptel.ac.in/noc23_cs126/preview}{NPTEL}}
    \item Data Science Math Skills \textit{(April 2020)} - \underline{\color{blue}\href{https://www.coursera.org/learn/datasciencemathskills}{Duke University, Coursera}} 
\end{itemize}}


\section{Education}
\customcventry{2021-2023}{\color{blue}\href{https://rkmvu.ac.in}{RKMVERI}}{MSc Data Science}{Belur, West Bengal, India} {}{}
{{Relevant Courses: Probability \& Stochastic Process, Data Structures \& Algorithms
, Statistics, Machine Learning, Deep Learning, Computer Vision, NLP, Optimization Techniques, Linear Algebra, Time Series Analysis, Survival Analysis, Cloud Computing, Multivariate Statistical Analysis, Data Mining, DBMS.} }
\\
\\
\customcventry{2017-2020}{\color{blue}\href{https://rkmvu.ac.in}{Vidyasagar University}}{BSc Mathematics}{Medinipur, West Bengal, India} {}{}
{{Relevant Courses: Set Theory, Calculus, Geometry \& Differential Equation, Higher Algebra, Real Analysis, Differential Equations \& Vector calculus, Group and Ring Theory, Theory of Equation, Graph Theory, PDE, ODE, DBMS, Operation Research, Numerical Methods.}}

\section{Personal Projects}
{\begin{itemize}[label=\textbullet]
\item {
\textbf{Fin-Bot: Advanced Agent based Financial Chatbot} \href{https://www.youtube.com/watch?v=yhfRhK09RCc}{\color{blue}{\faIcon{link}}}\\ 
\textit{(Domain: NLP, LLM, Generative AI, Deep Learning, RAG)} }
\\- Seamlessly integrated web search functionality ensuring comprehensive responses to queries.
\\- Implemented a custom vector database for efficient retrieval of financial news articles and concall transcripts.
\\- Employed LLM-equipped agent to direct user queries to relevant web or custom database, ensuring up-to-dated, comprehensive insights.
\end{itemize}}


{\begin{itemize}[label=\textbullet]
\item {
\textbf{SALES FORECASTING AND ANOMALY DETECTION ON WALMART SALES DATASET} \href{https://github.com/U77w41/Forcasting-and-Anomaly-Detection}{\color{blue}{\faIcon{link}}}\\ 
\textit{(Domain: Machine Learning, Time Series Analysis, Deep Learning)} }
\\- Used Factor Analysis for feature extraction.
\\- Concepts of time series, machine learning, and deep learning are used to predict future sales.
\\- Used unsupervised techniques to detect the anomalies.
\end{itemize}}
%
{\begin{itemize}[label=\textbullet]
\item {
\textbf{Deep Bidirectional LSTM Network for Textual Sentiment Analysis} \href{https://github.com/U77w41/Deep-Bidirectional-LSTM-Network-for-Textual-Sentiment-Analysis}{\color{blue}{\faIcon{link}}}\\ 
\textit{(Domain: Deep Learning, Sentiment Analysis, NLP, Web Scrapping)} }
\\- Integrated Twitter API for real-time tweet scraping.
\\- Utilized AsyncHTMLSession to scrape news articles from Google News.
\\- Leveraged Bi-LSTM architecture to process sequential data and extract meaningful features for sentiment classification.
\end{itemize}}
%
{\begin{itemize}[label=\textbullet]
\item {
\textbf{BRAIN TUMOUR CLASSIFICATION} \href{https://github.com/U77w41/Brain-Tumour-Classificaion}{\color{blue}{\faIcon{link}}}\\ 
\textit{(Domain: Computer Vision, Deep Learning, Optimization Techniques)} }
\\- Used Transfer Learning and Fine-tuned several pre-trained models.
\\- Explored different optimization algorithms such as Adam, RMSProp, SGD, GD, Adagrad etc.
\\- Applied snapshot learning technique to construct an ensemble predictive model.
\end{itemize}}
%
{\begin{itemize}[label=\textbullet]
\item {
\textbf{STATISTICAL ANALYSIS OF DIET, EXERCISE AND FITNESS} \href{https://github.com/U77w41/PDS-Project}{\color{blue}{\faIcon{link}}}\\ 
\textit{(Domain: EDA, Data Visualization, Data Analysis, Statistical Inference)} }
\\- Collected data using online surveys at different time frames.
\\- Employed descriptive statistics to summarize the key characteristics of the dataset.
\\- Used Power BI, Tableau, Excel, R, and Python for analysis and visualization.
\end{itemize}}


% \section{Achievements}
% {\begin{itemize}[label=\textbullet]
%     \item In 2023, achieved second place among 644 teams in the Brain Dead Deep Learning Competition, hosted by IIEST Shibpur Annual Tech Fest.
%     \item Kaggle Expert in three formats.
%     \item Acknowledged for exemplary research and discipline at the FY 2024 Vista Intelligence Annual Day event.
% \end{itemize}}

% \section{Languages}
% \begin{multicols}{2}
%     \begin{itemize}[label=\textbullet]
%     \item \textbf{English} [Native]
%     \item {\textbf{French} [Basic] - Learning}
%     \item {\textbf{Spanish} [Native]}
%     \item {\textbf{German} [Basic] - A1}
%     \end{itemize}
% \end{multicols}
\end{document}