\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black}
\nopagenumbers{}
\usepackage[utf8]{inputenc}
\usepackage{ragged2e}
\usepackage[scale=0.915]{geometry}
\usepackage{import}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{fontawesome5}
\usepackage[colorlinks = true,
        urlcolor  = blue,unicode]{hyperref}
\name{Ujjwal}{Chowdhury}
\newcommand*{\customcventry}[7][.13em]{
\begin{tabular}{@{}l}
{\bfseries #4} \
{\itshape #3}
\end{tabular}
\hfill
\begin{tabular}{l@{}}
{\bfseries #5} \
{\itshape #2}
\end{tabular}
\ifx&#7&%
\else{\
\begin{minipage}{\maincolumnwidth}%
\small#7%
\end{minipage}}\fi%
\par\addvspace{#1}}


\begin{document}
\makecvtitle
\vspace*{-16mm}
\begin{center}\textbf{Data Scientist, Research Analyst}\end{center}
\begin{center}
\begin{tabular}{ c c c }
\faMobile\enspace +91 8768686849 & \enspace\faIcon{envelope} \href{mailto:u77w41@gmail.com}{\color{black}{u77w41@gmail.com}} & \faHome\enspace Kolkata, India \\
\faLinkedin\enspace \color{blue} \href{https://www.linkedin.com/in/u77w41/}{in/u77w41} &
\faGithub\enspace \color{blue} \href{https://github.com/u77w41}{github.com/u77w41} & \enspace {$\mathbb{X}$}\enspace \color{blue} \href{https://twitter.com/UjjwalCh0wdhury}{UjjwalCh0wdhury}
\end{tabular}
\end{center}

\section{Profile}
{Experienced data scientist with a Master's degree in Data Science and over a year of practical experience. Specializes in NLP, Generative AI, and Stock Forecasting. Proficient in designing and developing innovative solutions using Artificial Intelligence, implementing ML models, and establishing collaborative frameworks with cross-functional teams to deliver impactful, data-driven insights. Skilled in fine-tuning and automating processes, analyzing outcomes, and effectively communicating findings to drive business impact.}

\section{Areas of Expertise}
{NLP, Generative AI, Machine Learning Algorithms,  Time Series Analysis, Algorithm Optimization, Statistical Analysis, Data Visualization, Model Development, Cross-functional Collaboration}

\section{Skills}
{\begin{itemize}[label=\textbullet]
\item {\textbf{Data Visualization:} Microsoft Power BI, Excel, Tableau, Seaborn, Plotly, Matplotlib}
\item {\textbf{Machine Learning and Deep Learning:} Feature Engineering, Model Development, 
Hyper-parameter Tuning, 
Neural Networks,
Reinforcement Learning,
Transfer Learning,
Optimization Techniques,
MLOps}
\item {\textbf{Tools/Frameworks:} 
Python,
R,
TensorFlow,
PyTorch,
Keras,
TFLite,
MLFlow,
PySpark,
PostgreSQL,
Azure,
AWS,
LangChain,
streamlit,
Docker,
Pydantic

}
\item {\textbf{Natural Language Processing:} Text Generation,
Sentiment Analysis,
Speech Recognition,
Named Entity Recognition,
Text Classification, LLM Prompt Engineering}
\item {\textbf{Computer Vision:} Image Processing, Object Detection, Image Classification, Image Segmentation, Image Generation}
\item {\textbf{Data Analysis and Mining:} Data Mining,
Web Scrapping,
Statistical Analysis,
Time Series Analysis,
Anomaly Detection,
Predictive Analytics,
Survival Analysis}
\item {\textbf{Soft Skills:} Problem-Solving, Teamwork, Active Listening, Adaptability, Communication, Analytical Thinking}
\end{itemize}}



\section{Professional Experience}
\customcventry{(Jan 2023 ‐ present)}{{\color{blue}\href{https://feedsense.vistaintelligence.ai/}{(Vista Intelligence Private Limited)}}}{AI Researcher}{Kolkata, 
India}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Led the NLP team, overseeing project developments and team operations.
\item Finetuned an RNN-Tranducer driven speech-to-text model to effectively capture Indian accents, decreasing the Word Error Rate from 56.8\% to 23.4\%.
\item Developed a live audio transcription model for real-time news analysis.
\item Developed a trade signal generator model integrating live audio, textual news articles, OHLC data, and quantitative techniques. Achieved over 75\% directional accuracy in generating Nifty F\&O trading signals, enabling informed trading decisions.
\item Created an auto question generator program to generate questions based on applicant CVs, aiding the hiring team.
\item Utilized OpenAI API with Langchain to develop a large document summarizer.
\item Employed a 4-bit quantized Mistral 7b LLM model for summarizing conference call conversations.
\end{itemize}}}

% \customcventry{01/2023 ‐ 05/2023}{{\color{blue}\href{https://www.google.com/}{(Synapse Solutions)}}}{Digital Account Manager,}{Las Vegas, NV}{}{
% {\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
% \item Implemented promotional activities such as re-targeting campaigns for e-commerce businesses.
% \item Monitored the performance of PPC campaigns through Google Adwords. 
% \item Managed and optimized PPC campaigns, resulting in a 5\% increase in click-through rates
% \end{itemize}}}

\section{Research \& Publication}
% \customcventry{March 2024}{\color{blue}\href{https://ieeexplore.ieee.org/document/10445412?source=authoralert}{IEEE Xplore}}
% {{Investigate How Market Behaves: Toward an Explanatory Multitasking Based Analytical Model for Financial Investments}}{DOI: 10.1109/ACCESS.2024.3369033} {}{}
{\begin{itemize}[label=\textbullet]
    \item Investigate How Market Behaves: Toward an Explanatory Multitasking Based Analytical Model for Financial Investments \textit{(IEEE Access, March 2024)} \color{blue}\href{DOI: 10.1109/ACCESS.2024.3369033}{DOI: 10.1109/ACCESS.2024.3369033}
\end{itemize}}

% Investigate How Market Behaves: Toward an Explanatory Multitasking Based Analytical Model for Financial Investments



\section{Courses \& Certifications}
{\begin{itemize}[label=\textbullet]
    \item Artificial Intelligence (AI) for Investments \textit{(April 2023)} - \underline{\color{blue}\href{https://onlinecourses.nptel.ac.in/noc23_mg63/preview}{NPTEL}}
    \item Cloud Computing and Distributed Systems \textit{(March 2023)} - \underline{\color{blue}\href{https://onlinecourses.nptel.ac.in/noc21_cs15/preview}{NPTEL}}
    \item NISM-Series-XV: Research Analyst \textit{(Feb. 2023)} - \underline{\color{blue}\href{https://www.nism.ac.in/}{National Institute of Securities Markets}}
    \item Data Base Management System \textit{(Oct. 2022)} - \underline{\color{blue}\href{https://onlinecourses.nptel.ac.in/noc21_cs04/preview}{NPTEL}}
    \item Deep Learning for Computer Vision \textit{(Oct. 2022)} - \underline{\color{blue}\href{https://onlinecourses.nptel.ac.in/noc23_cs126/preview}{NPTEL}}
    \item Data Science Math Skills \textit{(April 2020)} - \underline{\color{blue}\href{https://www.coursera.org/learn/datasciencemathskills}{Duke University, Coursera}} 
\end{itemize}}


\section{Education}
\customcventry{2021-2023}{\color{blue}\href{https://rkmvu.ac.in}{RKMVERI}}{MSc Data Science}{Belur, West Bengal, India} {}{}
{{Relevant Courses: Probability \& Stochastic Process, Data Structures \& Algorithms
, Statistics, Machine Learning, Deep Learning, Computer Vision, NLP, Optimization Techniques, Linear Algebra, Time Series Analysis, Survival Analysis, Cloud Computing, Multivariate Statistical Analysis, Data Mining, DBMS} }
\\
\\
\customcventry{2017-2020}{\color{blue}\href{https://rkmvu.ac.in}{Vidyasagar University}}{BSc Mathematics}{Medinipur, West Bengal, India} {}{}
{{Relevant Courses: Set Theory, Calculus, Geometry \& Differential Equation, Higher Algebra, Real Analysis, Differential Equations \& Vector calculus, Group and Ring Theory, Theory of Equation, Graph Theory, PDE, ODE, DBMS, Operation Research, Numerical Methods}}

\section{Personal Projects}
{\begin{itemize}[label=\textbullet]
\item {
\textbf{SALES FORECASTING AND ANOMALY DETECTION ON WALMART SALES DATASET} \href{https://github.com/U77w41/Forcasting-and-Anomaly-Detection}{\color{blue}{\faIcon{link}}}\\ 
\textit{(Domain: Machine Learning, Time Series Analysis, Deep Learning)} }
\\- Used Factor Analysis for feature extraction.
\\- Concepts of time series, machine learning, and deep learning are used to predict future sales.
\\- Used unsupervised techniques to detect the anomalies.
\end{itemize}}
%
{\begin{itemize}[label=\textbullet]
\item {
\textbf{Deep Bidirectional LSTM Network for Textual Sentiment Analysis} \href{https://github.com/U77w41/Deep-Bidirectional-LSTM-Network-for-Textual-Sentiment-Analysis}{\color{blue}{\faIcon{link}}}\\ 
\textit{(Domain: Deep Learning, Sentiment Analysis, NLP, Web Scrapping)} }
\\- Integrated Twitter API for real-time tweet scraping.
\\- Utilized AsyncHTMLSession to scrape news articles from Google News.
\\- Leveraged Bi-LSTM architecture to process sequential data and extract meaningful features for sentiment classification.
\end{itemize}}
%
{\begin{itemize}[label=\textbullet]
\item {
\textbf{BRAIN TUMOUR CLASSIFICATION} \href{https://github.com/U77w41/Brain-Tumour-Classificaion}{\color{blue}{\faIcon{link}}}\\ 
\textit{(Domain: Computer Vision, Deep Learning, Optimization Techniques)} }
\\- Used Transfer Learning and Fine-tuned several pre-trained models.
\\- Explored different optimization algorithms such as Adam, RMSProp, SGD, GD, Adagrad etc.
\\- Applied snapshot learning technique to construct an ensemble predictive model.
\end{itemize}}
%
{\begin{itemize}[label=\textbullet]
\item {
\textbf{STATISTICAL ANALYSIS OF DIET, EXERCISE AND FITNESS} \href{https://github.com/U77w41/PDS-Project}{\color{blue}{\faIcon{link}}}\\ 
\textit{(Domain: EDA, Data Visualization, Data Analysis, Statistical Inference)} }
\\- Collected data using online surveys at different time frames.
\\- Employed descriptive statistics to summarize the key characteristics of the dataset.
\\- Used Power BI, Tableau, Excel, R, and Python for analysis and visualization.
\end{itemize}}


\section{Achievements}
{\begin{itemize}[label=\textbullet]
    \item In 2023, achieved second place among 644 teams in the Brain Dead Deep Learning Competition, hosted by IIEST Shibpur Annual Tech Fest.
    \item Kaggle Expert in three formats.
    \item Acknowledged for exemplary research and discipline at the FY 2024 Vista Intelligence Annual Day event.
\end{itemize}}

% \section{Languages}
% \begin{multicols}{2}
%     \begin{itemize}[label=\textbullet]
%     \item \textbf{English} [Native]
%     \item {\textbf{French} [Basic] - Learning}
%     \item {\textbf{Spanish} [Native]}
%     \item {\textbf{German} [Basic] - A1}
%     \end{itemize}
% \end{multicols}
\end{document}